DP Problems of Interest

### 2012-10-01 docs/roadmap/problems.tex
local changes
Nussinov.

\documentclass[11pt]{article}
\usepackage{amssymb,amsmath,amsthm,hyperref,verbatim,pict2e,graphicx,marvosym,array,booktabs,nameref}
%\hypersetup{colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black}
\usepackage[usenames]{xcolor} % color names ,dvipsnames,svgnames,table
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\pagestyle{empty} % remove page numbers

@@

% ----------------------------------------------
\newpage
\subsection{Nussinov algorithm}\ol
\item Problem: folding a RNA string $S$ over itself $\left\lfloor |S| / 2 \right\rfloor = n$.
\item Matrices: $M_{n\times n}, B_{n \times n}$
\item Alphabets:\ul
	\item Input: $\Sigma(S)=\{A,C,G,U\}$.
	\item Cost matrix: $\Sigma(M)=\{0..n\}$
	\item Backtrack matrix: $\Sigma(B)=\{stop,W,S,SW, 1..n\}$
	\ule
\item Initialization: \ul
	\item Cost matrix: $ M_{(i,i)}=M_{(i,i-1)}=0$
	\item Backtrack matrix: $B_{(i,i)}=B_{(i,i-1)}=stop$
	\ule

{\color{red}
\item Recurrences (XXX: isn't it $\max_{i\le k < j}$ ?):
	\[M_{(i,j)}=\max\left\{\begin{array}{l|l}
		M_{(i+1,j-1)}+\omega(i,j) & SW\\
		M_{(i+1,j)} & S\\
		M_{(i,j-1)} & W\\
		\max_{i<k<j}M_{(i,k)}+M_{(k+1,j)} & k
	\end{array}\right\} = B_{(i,j)} \]
	With $\omega(i,j)=1$ if $i,j$ are complementary. 0 otherwise.
\item Backtracking: XXX
\item Visualisation: XXX
\item Optimizations: XXX
}
\ole

>>>>

\documentclass[11pt]{article}
\usepackage{amssymb,amsmath,amsthm,hyperref,verbatim,pict2e,graphicx,marvosym,array,booktabs,nameref}
\hypersetup{
	%colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black
	urlbordercolor=1 0 0,linkbordercolor=0 1 1, citebordercolor=0 1 1,
}
\usepackage[usenames]{xcolor} % color names ,dvipsnames,svgnames,table
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\pagestyle{empty} % remove page numbers

@@

% ----------------------------------------------
\newpage
\subsection{Nussinov algorithm}\ol
\item Problem: folding a RNA string $S$ over itself $\left\lfloor |S| / 2 \right\rfloor = n$.
\item Matrices: $M_{n\times n}, B_{n \times n}$
\item Alphabets:\ul
	\item Input: $\Sigma(S)=\{A,C,G,U\}$.
	\item Cost matrix: $\Sigma(M)=\{0..n\}$
	\item Backtrack matrix: $\Sigma(B)=\{stop,D,1..n\}$
	\ule
\item Initialization: \ul
	\item Cost matrix: $ M_{(i,i)}=M_{(i,i-1)}=0$
	\item Backtrack matrix: $B_{(i,i)}=B_{(i,i-1)}=stop$
	\ule
\item Recurrences:
	\[M_{(i,j)}=\max\left\{\begin{array}{l|l}
		M_{(i+1,j-1)}+\omega(i,j) & D\\
		\max_{i\le k<j}M_{(i,k)}+M_{(k+1,j)} & k
	\end{array}\right\} = B_{(i,j)} \]
	With $\omega(i,j)=1$ if $i,j$ are complementary. 0 otherwise.
\item Backtracking: Start the backtracking in $B_{(1,n)}$ and go backward. The backtracking is very similar to that of the matrix multiplication, except that we also introduce the diagonal matching.
\item Visualisation:
	\begin{center}\setlength{\unitlength}{.6cm}\begin{picture}(8,9)
		\put(-.7,6.5){\rotatebox{90}{First}}\put(-.4,6.4){\linethickness{1pt}\vector(0,-1){2}}
		\put(.2,8.2){Last}\put(1.5,8.4){\linethickness{1pt}\vector(1,0){2}}
		\Cfl{\Cg}\Cfd{\Cz}
		\Cd[0,1]{6,1}{2.8}\Cd[0,1]{6,2}{1.8}\Cd[0,1]{6,3}{0.8}
		\Cd[1,0]{3,4}{2.8}\Cd[1,0]{4,4}{1.8}\Cd[1,0]{5,4}{0.8}
		\Cd[1,1]{5,3}{0.8}
		\put(3.5,4.5){\line(3,-1){3}}\put(4.5,4.5){\line(2,-2){2}}\put(5.5,4.5){\line(1,-3){1}}
	\Cm\end{picture}\end{center}

\item Optimizations: note that this is very similar to the matrix multiplication except that we also need the diagonal one step backward, so the same optimization can apply.
\ole
